R for Clinical Study Reports and Submission

### 2021-10-07 project-management.Rmd

As a general principle, all the team members involved in a project
should take basic training on project management and understand how to work as
a software development team. @teamgeek provides some valuable tips on this topic.
As always, setting a clear goal and following a system development lifecycle
(SDLC) are essential.

>>>>

As a general principle, all the team members involved in a project
should take basic training on project management and understand how to work as
a development team. @teamgeek provides some valuable tips on this topic.
As always, setting a clear goal and following a system development lifecycle
(SDLC) are essential.
